Notes on Design and Implementation of Anglican

### 2015-07-29 paper/paper.tex
typos
another typo fixed

To realize potential danger of code size explosion, consider
CPS transformation of code
\begin{lstlisting}[frame=single,language=Anglican, basicstyle=\scriptsize\ttfamily, showstringspaces=false]
(if (adult? person)
  (if (male? person)
	 (choose-beer)
	 (choose_wine))
  (choose-juice))
\end{lstlisting}
with continuation 
\begin{lstlisting}[frame=single,language=Anglican, basicstyle=\scriptsize\ttfamily, showstringspaces=false]
(fn [choice _]
  (case (kind choice)
    :beer (beer-jar choice)
    :wine (wine-glass choice)
    :juice (juice-bottle choice)))
\end{lstlisting}
The code of continuation, represented by an \texttt{fn} form, will be
repeated three times. In general, CPS code can grow extremely
large if symbolic continuations are inserted repeatedly.

@@

\textit{Memoization} is often implemented on top of a mutable
dictionary, where the key is the argument list and the value is
the returned value. However, there are no mutable data
structures in a probabilistic program, hence \texttt{mem}'s
memory is stored as a nested dictionary in the program state
(function \texttt{mem-cps}).  Each memoized function receives a
unique automatically generated identifier. Each time a memoized
function is called, one of two continuations is chosen,
depending on whether the same function (a function with the same
identifier) was previously called in the same run of the
probabilistic program with the same arguments. If the memoized
result is available, the continuation of the memoized function
call is immediately called with the stored result. Otherwise,
the argument of \texttt{mem} is called with a continuation that
first creates an updated state with the memoized result, and
then calls the `outer' continuation with the result and the
updated state.

>>>>

To realize potential danger of code size explosion, consider
CPS transformation of code
\begin{lstlisting}[frame=single,language=Anglican, basicstyle=\scriptsize\ttfamily, showstringspaces=false]
(if (adult? person)
  (if (male? person)
	 (choose-beer)
	 (choose_wine))
  (choose-juice))
\end{lstlisting}
with continuation 
\begin{lstlisting}[frame=single,language=Anglican, basicstyle=\scriptsize\ttfamily, showstringspaces=false]
(fn [choice _]
  (case (kind choice)
    :beer (beer-jar choice)
    :wine (wine-glass choice)
    :juice (juice-bottle choice)))
\end{lstlisting}
The code of the continuation, represented by an \texttt{fn}
form, will be repeated three times. In general, CPS code can
grow extremely large if symbolic continuations are inserted
repeatedly.

@@

\textit{Memoization} is often implemented on top of a mutable
dictionary, where the key is the argument list and the value is
the returned value. However, there are no mutable data
structures in a probabilistic program, hence \texttt{mem}'s
memory is stored as a nested dictionary in the program state
(function \texttt{mem-cps}).  Every memoized function gets a
unique automatically generated identifier. Each time a memoized
function is called, one of two continuations is chosen,
depending on whether the same function (a function with the same
identifier) was previously called in the same run of the
probabilistic program with the same arguments. If the memoized
result is available, the continuation of the memoized function
call is immediately called with the stored result. Otherwise,
the argument of \texttt{mem} is called with a continuation that
first creates an updated state with the memoized result, and
then calls the `outer' continuation with the result and the
updated state.
